CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex
edited paper.tex

>>>>

\subsection{Walk through of one question}
\begin{itemize}
\item Initial setup of the Q/A system
    \begin{itemize}
    \item We collect all the documents that may contain the answer for all qids (20 documents per qid)
    \item We then run the chunker on the document text creating answer candidate phrases
    \item We save the chunker results to a set of files
    \end{itemize}
\item We are given a question id
\item We retrieve the question text from the provided input file
\item We read the chunker results 
    \begin{itemize}
    \item We filter out all candidate answers that are not noun phrases
    \item We also filter out candidate answers not within 50 bytes of the aligned question in the document
    \end{itemize}
\item We feed the filtered answers through our answer evaluators specifically
    \begin{itemize}
    \item punctuation location
    \item novelty factor
    \item A combination of both
    \end{itemize}
\item The scores of the evaluators are fed into the supervised classification algorithm
    \begin{itemize}
    \item Spectral Regression Discriminant Analysis 
    \item This gives us a confidence measure
    \end{itemize}
\item Sort by confidence measure 
\item In descending order by confidence measure, pack them into 50-byte answers which are our final outputs
\item The answers are then passed into our scorer
\end{itemize}
